Capstone Movielens Report

### 2025-09-22 reports/capstone-movielens.site/01.intro.Rmd

Now, note the expressions below which confirm the fact explained in [Section _23.1.1 Movielens data_](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#movielens-data) of the _Course Textbook_[@IDS2] that not every user rated every movie:
```{r}
max_possible_ratings <- n_movies*n_users
sprintf("Maximum possible ratings: %s", max_possible_ratings)
sprintf("Rows in `edx` dataset: %s", dim_edx[1])
sprintf("Not every movie was rated: %s", max_possible_ratings > dim_edx[1])

>>>>

Now, note the expressions below which confirm the fact explained in [Section _23.1.1 Movielens data_](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#movielens-data) of the _Course Textbook_[@IDS2_23-1-1] that not every user rated every movie:
```{r}
max_possible_ratings <- n_movies*n_users
sprintf("Maximum possible ratings: %s", max_possible_ratings)
sprintf("Rows in `edx` dataset: %s", dim_edx[1])
sprintf("Not every movie was rated: %s", max_possible_ratings > dim_edx[1])

### 2025-09-22 reports/capstone-movielens.site/02-0.methods.Rmd
Report review; working on UMGYE Model Building (in progress)

# Methods / Analysis
::: {.noteblock data-latex=""}
All the source code of the R-scripts is available on the project's [GitHub repository](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/tree/main/r/src)[@edx_capstone_movielens]. 
:::

@@

#### `clamp` function
\

>>>>

# Methods and Analysis
::: {.noteblock data-latex=""}
All the source code of the R-scripts is available on the project's [GitHub repository](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/tree/main/r/src)[@edx_capstone_movielens]. 
:::

@@

#### [clamp](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L4) function {#func.clamp}
\

### 2025-09-22 reports/capstone-movielens.site/02.4.UE-model.Rmd
Section `UMGYE Model Building` completed.

Finally, we are ready to compute the `RMSE` (additionally using the [clamp](#func.clamp) helper function we described above to keep predictions in the proper range):

@@

::: {.noteblock data-latex=""}
For the _Mean Squared Errors_ data visualization we use the custom data visualization function [data.plot](#func.data.plot) described in the [Data Helper Functions](#appndx_a.data_helper.functions) section of the [Appendix] to this report, which is defined in the [Data Visualization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L447) section of the [data.helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L592) script on _GitHub_.
:::

@@

::: {.noteblock data-latex=""}
The full source code of the _User Effect Model RMSE_ computation is available in the [Compute RMSE for User Effect Model](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L655) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R) script on _GitHub_.
:::

>>>>

@@

::: {.noteblock data-latex=""}
For the _Mean Squared Errors_ data visualization we use the custom data visualization function [data.plot](#func.data.plot) described in the [Data Helper Functions](#appndx_a.data_helper.functions) section of the [Appendix] to this report.

The full source code of the _User Effect Model RMSE_ computation is available in the [Compute RMSE for User Effect Model](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L655) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R) script on _GitHub_.
:::

@@

::: {.noteblock data-latex=""}
Here use the [RMSEs.AddRow](#func.RMSEs.AddRow) and [RMSE_kable](#func.RMSE_kable) functions described in the [Common Helper Functions: Result RMSEs Table] section of the [Appendix] to this report.
:::
